\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-03 doc/sw-system.tex
Data sesction done, closed #31

In this paper, we describe the \sw website, an online system that enables 
crowd-sourced gravitational lens detection by inviting volunteers to classify
astronomical survey images as containing lens candidates or not.  In a
companion paper we will present the new gravitational lenses discovered in our
first experimental lens search, and begin to investigate the differences
between lens detections made in \sw and those made with automated techniques.
Here though, we try to answer the following questions:

@@

Our basic method in this paper is to analyze the performance of the \sw system
on a ``training set'' of simulated lenses and known non-lenses. This allows us
to estimate completeness and purity with respect to gravitational lenses that
have the same properties of the training set. In the companion paper we carry
out similar tests but with a sample of known (real) lenses {\it in situ}.

@@

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
features they have seen either before they submit their classification, or
after, if they ``favorite'' the subject. There is no ``back'' button: each
volunteer may only classify a given subject once. However, the presence of an
option to see what others think about any given subject before submitting your
own classification means that the classifications may not be  strictly
independent; the advantage of this system is that volunteers can learn from
others what constitutes a good lens candidate. In practice, we might expect
this to be a relatively unimportant educational resource, given the explicit
training we provide for the volunteers, which we describe in the next section.

@@

@@

@@

Definitions: training subjects and test subjects. Sims and duds.

@@

Describe survey. Refs.

Why this one? Good IQ, deep, colorful, homogeneous. Precursor to Stage III and
IV imaging surveys, DES, KIDS, LSST etc. Already searched by robots: enables
comparison of techniques. Lenses not yet found by robots, detectable by
humans?

Blind search strategy.
Preparation of data: divide survey into overlapping tiles.

@@

Presentation of images. Uniform scales, to build intuition and avoid rescales
due to bright objects. Arcsinh stretch, to bring out low SB features. 
Approximately optimized, how? Examples of images.

@@

In this section we outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source 
SWAP code is available from 
\texttt{https://github.com/drphilmarshall/SpaceWarps}}

>>>>

In this paper, we describe the \sw website, an online system that enables 
crowd-sourced gravitational lens detection by inviting volunteers to classify
astronomical survey images as containing lens candidates or not.  In a
companion paper (More et al, in preparation, herafter \papertwo) we will
present the new gravitational lenses discovered in our first experimental lens
search, and begin to investigate the differences between lens detections made
in \sw and those made with automated techniques. Here though, we try to answer
the following questions:

@@

Our basic method in this paper is to analyze the performance of the \sw system
on a ``training set'' of simulated lenses and known non-lenses. This allows us
to estimate completeness and purity with respect to gravitational lenses that
have the same properties of the training set. In \papertwo we carry
out similar tests but with a sample of known (real) lenses {\it in situ}.

@@

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once.
However, the presence of an option to see what others think about any given
subject before submitting your own classification means that the
classifications may not be  strictly independent; the advantage of this system
is that volunteers can learn from others what constitutes a good lens
candidate. In practice, we might expect this to be a relatively unimportant
educational resource, given the explicit training we provide for the
volunteers, which we describe in the next section.

@@

In \Fref{fig:training-gallery} we show 12 example training images from the
first \sw project (\Sref{sec:data} below).

\todo{Phil, Aprajita}{Make gallery of 6 stage 2 sims and 6 stage 2 duds, to
give the reader a feel for what the sims look like, and also how the images
were presented, stretch and scale-wise.}

@@

\todo{Phil}{write this section (\#31)}

@@

We refer the reader to \papertwo for the details of the particular set of
imaging survey data used in this first \sw project. Here, we summarize very
briefly the choices that were made, in order to provide the context for our
general description and illustrations of the \sw system.

@@

The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered XXX square degrees of
approximately equatorial sky, in four patches distributed in right ascension,
over the course of N years. With homegeneous image quality of, typically, X
arcsec (in the $i$-band), and reaching limiting magnitudes of XX-XX in the
$ugriz$ filter set, this survey has yielded several dozen new gravitational
lenses on both galaxy and group scales \citep{}. The quality of the data,
combined with the presence of these comparison ``known lens'' samples, made
this a natural choice against which to develop and test the \sw system. The
CFHTLS is also well-representative of the data quality expected from several
next-generation sky surveys, such as DES, KiDS, HSC and LSST.

In order to investigate the completeness of the previous, semi-automated, lens
searches in the CFHTLS area, we designed a ``blind search.'' We divided the
mosaiced images into some 430,000 equal size, overlapping tiles, approximately
70~arcsec on a side. Each of these images is a ``test image'' (as opposed to a
``training image''). In future, larger area projects we expect to implement
the rather different strategy of producing image tiles centred on particular
pre-selected ``targets,'' to make for a more efficient (but less complete)
survey. We do not expect the performance of citizen image inspectors to change
significantly between these strategies: to first order, both strategies
require the inspectors to learn what lenses look like, and then search the
presented images for similar features.

@@

The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
quality, and we chose to focus on this set (although the $u$ and $z$-band
images were also available for inspection in Talk). We made colour composite
images using publically-available code\footnote{The open source  colour image
composition code used in this work is available from
\texttt{http://github.com/drphilmarshall/HumVI}} following the prescription of
\citet{LuptonEtal}. Specifically, we first rescaled the pixel values of each
channel image into flux units, and then applied an arcsinh stretch. The
stretch parameters were chosen using a small random sample of images, to
ensure that the background noise was just visible,  and that the centres of
bright, intermediate resdhift galaxies were not saturated. The color scales
were chosen to maximize the contrast between faint extended objects. These
parameters were then fixed during the production of all the tiles, in order to
allow straightforward comparison between one image and another, and for
intuition to be built up about the appearance of stars and galaxies across the
survey. Alternative algorithms, such as adjusting the stretch and scale
dynamically according to, for example, the root-mean-square pixel value in
each image, can lead to better presentation of bright objects, but in doing so
they tend to hide the faint features in those images: we needed to optimize
the detectability of these faint features.   Examples of CFHTLS training set
images can be seen in \Fref{fig:training-gallery}.

@@

Having described the classification interface, the training images and the
test images,  we now outline our methodology for interpreting the interactions
of the volunteers with the identification interface, and then describe how we
applied this methodology in the two classification stages in the CFHTLS
project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source 
SWAP code is available from 
\texttt{https://github.com/drphilmarshall/SpaceWarps}}
